Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-03 WSSSPE4_report/participants.tex
turning off email of participants

\href{mailto:mjab@kth.se}{Mark Abraham} & SciLifeLab, KTH, Sweden\\
\href{mailto:Aseel.aldabjan@student.manchester.ac.uk}{Aseel Aldabjan} & University of Manchester\\
\href{mailto:aallen@ascl.net}{Alice Allen} & Astrophysics Source Code Library\\
\href{mailto:gdallen@illinois.edu}{Gabrielle Allen} & NCSA/University of Illinois\\
\href{mailto:pau.andrio@bsc.es}{Pau Andrio} & Barcelona Supercomputing Center\\
\href{mailto:bangerth@colostate.edu}{Wolfgang Bangerth} & Colorado State University\\
\href{mailto:radovan.bast@uit.no}{Radovan Bast} & UiT The Arctic University of Norway, Nordic e-Infrastructure Collaboration\\
\href{mailto:roman.bauer@newcastle.ac.uk}{Roman Bauer} & Newcastle University\\
\href{mailto:sbrandt@cct.lsu.edu}{Steven Brandt} & Louisiana State University\\
\href{mailto:lukas.johannes.breitwieser@cern.ch}{Lukas Johannes Breitwieser} & CERN\\
\href{mailto:echen35@illinois.edu}{Emily Chen} & NCSA/University of Illinois Urbana--Champaign\\
\href{mailto:childers@pitt.edu}{Bruce Childers} & University of Pittsburgh\\
\href{mailto:M.Croucher@Sheffield.ac.uk}{Mike Croucher} & University of Sheffield\\
\href{mailto:michael.crusoe@gmail.com}{Michael R. Crusoe} & Common Workflow Language Project\\
\href{mailto:stephan.druskat@hu-berlin.de}{Stephan Druskat} & Humboldt-Universit\"{a}t zu Berlin\\
\href{mailto:adubey@anl.gov}{Anshu Dubey} & Argonne National Laboratory\\
\href{mailto:tim.dunne@knowinnovation.com}{Tim Dunne} & KnowInnovation\\
\href{mailto:Peter.Elmer@cern.ch}{Peter Elmer} & Princeton University\\
\href{mailto:iain.emsley@oerc.ox.ac.uk}{Iain Emsley} & University of Oxford\\
\href{mailto:fangohr@soton.ac.uk}{Hans Fangohr} & University of Southampton\\
\href{mailto:stuart@stuartgeiger.com}{Stuart Geiger} & Berkeley Institute for Data Science\\
\href{mailto:sandra.gesing@nd.edu}{Sandra Gesing} & University of Notre Dame\\
\href{mailto:carole.goble@manchester.ac.uk}{Carole Goble} & University of Manchester, Software Sustainability Institute\\
\href{mailto:goodale@gmail.com}{Tom Goodale} & Independent\\
\href{mailto:gwilliamsc@cardiff.ac.uk}{Christopher Gwilliams} & Cardiff University\\
\href{mailto:w.vanhage@esciencecenter.nl}{Willem van Hage} & Netherlands eScience Center\\
\href{mailto:robert.haine@manchester.ac.uk}{Robert Haines} & University of Manchester\\
\href{mailto:j.hetherington@ucl.ac.uk}{James Hetherington} & University College London\\
\href{mailto:s.hettrick@software.ac.uk}{Simon Hettrick} & Software Sustainability Institute\\
\href{mailto:N.ChueHong@software.ac.uk}{Neil Chue Hong} & Software Sustainability Institute\\
\href{mailto:ljhwang@ucdavis.edu}{Lorraine Hwang} & UC Davis, CIG\\
\href{mailto:rayi@renci.org}{Ray Idaszak} & RENCI, University of North Carolina at Chapel Hill\\
\href{mailto:caroline.jay@manchester.ac.uk}{Caroline Jay} & University of Manchester\\
\href{mailto:bjimenez@bsc.es}{Brian Jimenez} & Barcelona Supercomputing Center\\
\href{mailto:rafael.jimenez@elixir-europe.org}{Rafael C Jimenez} & ELIXIR Hub, UK\\
\href{mailto:d.katz@ieee.org}{Daniel S Katz} & University of Illinois Urbana--Champaign\\
\href{mailto:dominic.kempf@iwr.uni-heidelberg.de}{Dominic Kempf} & Heidelberg University\\
\href{mailto:p.lago@vu.nl}{Patricia Lago} & Vrije Universiteit Amsterdam\\
\href{mailto:liu@hood.edu}{Xinlian Liu} & Hood College\\
\href{mailto:hannes.loeffler@stfc.ac.uk}{Hannes Loeffler} & STFC\\
\href{mailto:knarf@cct.lsu.edu}{Frank L\"{o}ffler} & Louisiana State University\\
\href{mailto:tengyu.ma@vanderbilt.edu}{Tengyu Ma} & Vanderbilt University\\
\href{mailto:rhmcdona@indiana.edu}{Robert H McDonald} & Indiana University\\
\href{mailto:chris.mentzel@moore.org}{Chris Mentzel} & Moore Foundation\\
\href{mailto:costa.michailidis@knowinnovation.com}{Constantinos Michailidis} & KnowInnovation\\
\href{mailto:jmiller@perimeterinstitute.ca}{Jonah Miller} & Perimeter Institute of Theoretical Physics\\
\href{mailto:mosse@cs.pitt.edu}{Daniel Mosse} & University of Pittsburgh\\
\href{mailto:august.muench@aas.org}{August (Gus) Muench} & American Astronomical Society\\
\href{mailto:unangi2@illinois.edu}{Udit Nangia} & University of Illinois Urbana--Champaign\\
\href{mailto:a.nenadic@manchester.ac.uk}{Aleksandra Nenadic} & University of Manchester, SSI\\
\href{mailto:Kyle.Niemeyer@oregonstate.edu}{Kyle Niemeyer} & Oregon State University\\
\href{mailto:nunezco2@illinois.edu}{Santiago N\'u\~nez-Corrales} & University of Illinois Urbana--Champaign\\
\href{mailto:d.a.orchard@kent.ac.uk}{Dominic Orchard} & University of Kent\\
\href{mailto:chico@puc-rio.br}{Francisco Queiroz} & Pontifical Catholic University of Rio de Janeiro\\
\href{mailto:fons.rademakers@cern.ch}{Fons Rademakers} & CERN\\
\href{mailto:karthik.ram@berkeley.edu}{Karthik Ram} & University of California, Berkeley\\
\href{mailto:samuel.relton@manchester.ac.uk}{Sam Relton} & University Of Manchester\\
\href{mailto:thomas.robitaille@gmail.com}{Tom Robitaille} & Freelance\\
\href{mailto:jeansalac@virginia.edu}{Jean Salac} & University of Virginia\\
\href{mailto:janos.sallai@vanderbilt.edu}{Janos Sallai} & Vanderbilt University\\
\href{mailto:prabhjyot10@gmail.com}{Prabhjyot (Singh) Saluja} & Southwestern Oklahoma State University\\
\href{mailto:eseidel@cs.ucsd.edu}{Eric Seidel} & University of California, San Diego\\
\href{mailto:sameer@cs.uoregon.edu}{Sameer Shende} & University of Oregon\\
\href{mailto:raniere.silva@software.ac.uk}{Raniere Silva} & University of Manchester\\
\href{mailto:shoaib.sufi@software.ac.uk}{Shoaib Sufi} & University of Manchester, Software Sustainability Institute\\
\href{mailto:chris.sweet@nd.edu}{Chris Sweet} & University of Notre Dame\\
\href{mailto:py12rw@leeds.ac.uk}{Rob Welch} & University of Leeds\\
\href{mailto:Christopher.Woods@bristol.ac.uk}{Christopher Woods} & University of Bristol\\

>>>>

Mark Abraham & SciLifeLab, KTH, Sweden\\
Aseel Aldabjan & University of Manchester\\
Alice Allen & Astrophysics Source Code Library\\
Gabrielle Allen & NCSA/University of Illinois\\
Pau Andrio & Barcelona Supercomputing Center\\
Wolfgang Bangerth & Colorado State University\\
Radovan Bast & UiT The Arctic University of Norway, Nordic e-Infrastructure Collaboration\\
Roman Bauer & Newcastle University\\
Steven Brandt & Louisiana State University\\
Lukas Johannes Breitwieser & CERN\\
Emily Chen & NCSA/University of Illinois Urbana--Champaign\\
Bruce Childers & University of Pittsburgh\\
Mike Croucher & University of Sheffield\\
Michael R. Crusoe & Common Workflow Language Project\\
Stephan Druskat & Humboldt-Universit\"{a}t zu Berlin\\
Anshu Dubey & Argonne National Laboratory\\
Tim Dunne & KnowInnovation\\
Peter Elmer & Princeton University\\
Iain Emsley & University of Oxford\\
Hans Fangohr & University of Southampton\\
Stuart Geiger & Berkeley Institute for Data Science\\
Sandra Gesing & University of Notre Dame\\
Carole Goble & University of Manchester, Software Sustainability Institute\\
Tom Goodale & Independent\\
Christopher Gwilliams & Cardiff University\\
Willem van Hage & Netherlands eScience Center\\
Robert Haines & University of Manchester\\
James Hetherington & University College London\\
Simon Hettrick & Software Sustainability Institute\\
Neil Chue Hong & Software Sustainability Institute\\
Lorraine Hwang & UC Davis, CIG\\
Ray Idaszak & RENCI, University of North Carolina at Chapel Hill\\
Caroline Jay & University of Manchester\\
Brian Jimenez & Barcelona Supercomputing Center\\
Rafael C Jimenez & ELIXIR Hub, UK\\
Daniel S Katz & University of Illinois Urbana--Champaign\\
Dominic Kempf & Heidelberg University\\
Frank L\"{o}ffler & Louisiana State University\\
Patricia Lago & Vrije Universiteit Amsterdam\\
Xinlian Liu & Hood College\\
Hannes Loeffler & STFC\\
Tengyu Ma & Vanderbilt University\\
Robert H McDonald & Indiana University\\
Chris Mentzel & Moore Foundation\\
Constantinos Michailidis & KnowInnovation\\
Jonah Miller & Perimeter Institute of Theoretical Physics\\
Daniel Mosse & University of Pittsburgh\\
August (Gus) Muench & American Astronomical Society\\
Santiago N\'u\~nez-Corrales & University of Illinois Urbana--Champaign\\
Udit Nangia & University of Illinois Urbana--Champaign\\
Aleksandra Nenadic & University of Manchester, SSI\\
Kyle Niemeyer & Oregon State University\\
Dominic Orchard & University of Kent\\
Francisco Queiroz & Pontifical Catholic University of Rio de Janeiro\\
Fons Rademakers & CERN\\
Karthik Ram & University of California, Berkeley\\
Sam Relton & University Of Manchester\\
Tom Robitaille & Freelance\\
Jean Salac & University of Virginia\\
Janos Sallai & Vanderbilt University\\
Prabhjyot (Singh) Saluja & Southwestern Oklahoma State University\\
Eric Seidel & University of California, San Diego\\
Sameer Shende & University of Oregon\\
Raniere Silva & University of Manchester\\
Shoaib Sufi & University of Manchester, Software Sustainability Institute\\
Chris Sweet & University of Notre Dame\\
Rob Welch & University of Leeds\\
Christopher Woods & University of Bristol\\
